---
output:
  github_document:
    html_preview: false
bibliography:
- packages.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

  library(magrittr)

```

# `envRaster`: Create and interact with environmental rasters

<!-- badges: start -->
<!-- badges: end -->

The goal of `envRaster` is to simplify the making of environmental rasters for use in other workflows. This includes making:

* a simple base raster to use as extent, resolution and crs when making environmental rasters
* regular cubes of earth observation data and climate data
    + capture meta data in paths
    + extract meta data from paths
* landform classification from digital terrain models (old code not updated recently)
* tibbles of environmental data extracted to points

There are better packages for doing most of this, particularly [sits](https://cran.r-project.org/web/packages/sits/index.html), but also  [stars](https://cran.r-project.org/web/packages/stars/index.html), [terra](https://cran.r-project.org/web/packages/terra/index.html) and [gdalcubes](https://cran.r-project.org/web/packages/gdalcubes/index.html).

Key packages used in `envRaster` are terra `r envReport::cite_package("terra")`, rstac `r envReport::cite_package("rstac")` and gdalcubes `r envReport::cite_package("gdalcubes")`.

Default settings in `envRaster` tend to favour South Australian settings (e.g. the output epsg for `make_base_grid()`).


## Installation

`envFunc` is not on [CRAN](https://CRAN.R-project.org).

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Acanthiza/envRaster")
```

Load `envRaster`

```{r}
library("envRaster")
```

# References

