
```{r {{thisID}}}

thisID <- "{{thisID}}" # use in figure references and file names

```

```{r dataSetup{{thisID}}}

this_env_data <- env_df_source |>
  dplyr::filter(env_id == thisID)

thisName <- this_env_data$name
thisLayer <- paste0(this_env_data$layer, " ", this_env_data$func)
thisType <- this_env_data$type
thisDesc <- this_env_data$description

thisDatSummary <- env_df_source %>%
  dplyr::filter(env_id == thisID) %>%
  dplyr::mutate(dplyr::across(tidyselect::matches("^q"), \(x) round(x, 2)))

thisRas <- terra::rast(thisDatSummary$path[[1]])

use_extent <- extent_sf |>
  sf::st_transform(crs = sf::st_crs(thisRas))

terra::window(thisRas) <- terra::ext(use_extent)

terra::set.names(thisRas, thisLayer)

use_units <- if(!is.na(thisDatSummary$units)) paste0(" ", unique(thisDatSummary$units)) else ""

# extra text ------
extra_text <- NULL

if(grepl("distance", thisLayer)) {
  
  ## distance ------
  
  extra_text <- paste0(extra_text
                       , " "
                       , envFunc::first_up(thisLayer)
                       , " was capped at "
                       , max(thisDatSummary$max)
                       , " m."
                       )
  
}

```

#### `r thisLayer`: `r thisDesc` {#`r tolower(thisName)`}

Table \@ref(tab:envInfo{{thisID}}) lists important details for `r thisLayer`.

Figure \@ref(fig:envHist{{thisID}}) shows the distribution of values in `r thisLayer`. The median value for `r thisLayer` within `r report_name` was `r thisDatSummary$q50``r use_units` with an inter-quartile range between `r thisDatSummary$q25` and `r thisDatSummary$q75``r use_units`.`r if(!is.null(extra_text)) extra_text`

Figure \@ref(fig:envMap{{thisID}}) shows the spatial distribution of values in `r thisLayer`.

```{r envInfo{{thisID}}}

thisDatSummary |>
  dplyr::select(source, collection, layer, `function` = func
                , `earliest date` = start_date, period
                , `resolution (m)` = res
                , notes
                , `indicates/useful for` = indicates
                , scale
                , offset
                , units
                , dplyr::where(is.numeric)
                ) |>
  dplyr::rename_with(.fn = \(x) gsub("^q(\\d{2})", paste0("\\1th percentile"), x)
                     , .cols = tidyselect::matches("^q")
                     ) |>
  t() |>
  as.data.frame() |>
  tibble::rownames_to_column() |>
  purrr::set_names(c("name", "value")) |>
  env_kable_extra(caption = paste0("Key information on ", thisLayer)
                  , align = "lr"
                  )

```

<br>

```{r envHist{{thisID}}, fig.cap = paste0("Distribution of values in the ", thisType, " layer `", thisLayer, "` ", thisDesc)}

hist_data <- random_env |>
  dplyr::select(all_of(thisName)) %>%
  dplyr::rename(value = 1) %>%
  dplyr::mutate(name = thisName) %>%
  dplyr::left_join(thisDatSummary)

ggplot(hist_data, aes(value)) +
  geom_density() +
  theme(axis.text.y=element_blank()
        , axis.ticks.y=element_blank()
        ) +
  labs(y = "frequency"
       , x = thisName
       )

```

<br>

```{r envMap{{thisID}}, fig.height = 7, fig.cap = paste0("Map of ", thisLayer)}

  terra::plot(thisRas)

```

<br>
